Computable Poincar\'e--Friedrichs constants for the $L^{p}$ de Rham complex over convex domains and domains with shellable triangulations

### 2024-10-04 main.tex
additional graphics

\begin{figure}[h]
\centerline{\includegraphics[width=0.2\textwidth]{revision/homotopic_ball.jpg} \quad \includegraphics[width=0.2\textwidth]{revision/homotopic_ball.jpg}}
\caption{A manifold triangulation (left) and not a manifold triangulation (right)}
\label{figure:not_manifold_triang}
\end{figure}

>>>>

\begin{figure}[h]
% \centerline{\includegraphics[width=0.2\textwidth]{revision/homotopic_ball.jpg} \quad \includegraphics[width=0.2\textwidth]{revision/homotopic_ball.jpg}}
\centering
\begin{tikzpicture}[scale=0.8]
    % Coordinates of the main outer triangle
    \coordinate (B0)  at (0,-1); % Bottom left
    \coordinate (BL)  at (-3,0); % Bottom right
    \coordinate (BR)  at (3,0); % Bottom right
    \coordinate (CLL) at (-3,2); % Bottom left
    \coordinate (CL)  at (-1,1); % Bottom right
    \coordinate (CR)  at ( 1,1); % Bottom right
    \coordinate (CRR) at ( 3,2); % Bottom right
    \coordinate (Z)   at (0,3.5); % Top
    \coordinate (ML) at  (-0.8,2.2);% ($(CL)!0.3!(Z)$);
    \coordinate (MR) at  ( 0.8,2.2);% ($(CR)!0.6!(Z)$);
    \draw[thick,fill=gray!25] (B0) -- (CL) -- (CR) -- cycle;
    \draw[thick,fill=gray!25] (B0) -- (CL) -- (BL) -- cycle;
    \draw[thick,fill=gray!25] (BL) -- (CL) -- (CLL) -- cycle;
    \draw[thick,fill=gray!25] (B0) -- (CR) -- (BR) -- cycle;
    \draw[thick,fill=gray!25] (BR) -- (CR) -- (CRR) -- cycle;
    \draw[thick,fill=gray!25] (ML) -- (CL) -- (CLL) -- cycle;
    \draw[thick,fill=gray!25] (MR) -- (CR) -- (CRR) -- cycle;
    \draw[thick,fill=gray!25] (Z) -- (ML) -- (CLL) -- cycle;
    \draw[thick,fill=gray!25] (Z) -- (MR) -- (CRR) -- cycle;
    \draw[thick,fill=gray!25] (Z) -- (ML) -- (MR) -- cycle;
\end{tikzpicture}
\qquad
\begin{tikzpicture}[scale=0.8]
    % Coordinates of the main outer triangle
    \coordinate (B0)  at (0,-1); % Bottom left
    \coordinate (BL)  at (-3,0); % Bottom right
    \coordinate (BR)  at (3,0); % Bottom right
    \coordinate (CLL) at (-3,2); % Bottom left
    \coordinate (CL)  at (-1,1); % Bottom right
    \coordinate (CR)  at ( 1,1); % Bottom right
    \coordinate (CRR) at ( 3,2); % Bottom right
    \coordinate (Z)   at (0,3.5); % Top
    \draw[thick,fill=gray!25] (B0) -- (CL) -- (CR) -- cycle;
    \draw[thick,fill=gray!25] (B0) -- (CL) -- (BL) -- cycle;
    \draw[thick,fill=gray!25] (BL) -- (CL) -- (CLL) -- cycle;
    \draw[thick,fill=gray!25] (B0) -- (CR) -- (BR) -- cycle;
    \draw[thick,fill=gray!25] (BR) -- (CR) -- (CRR) -- cycle;
    \draw[thick,fill=gray!25] (Z) -- (CL) -- (CLL) -- cycle;
    \draw[thick,fill=gray!25] (Z) -- (CR) -- (CRR) -- cycle;
\end{tikzpicture}

\caption{Left: manifold triangulation of an anulus. Right: not a manifold triangulation.}
\label{figure:not_manifold_triang}
\end{figure}
